Progress Report for CSS 586 Course Project: \\ Modeling Latent Patterns in Music

### 2021-05-02 papers/progress/alex/progress-alex.tex
add pianoroll to numpy function

The result of this preprocessing is that each training example will be
a 3D tensor of shape (tracks x notes x ticks) and stacking the
training examples will produce a 4D tensor.

>>>>

The result of this preprocessing is that each training example will be
a 3D tensor of shape (tracks x ticks x pitches) and stacking the
training examples will produce a 4D tensor.
